### 2012-12-27 annualreports/2012/balancesheet.tex
More 2012 report updates

\begin{center}
\begin{tabular}{  l  r  r r r}
\toprule
                            & \multicolumn{2}{c}{2012} &  \multicolumn{2}{c}{2011} \\
\cmidrule(r){2-3} \cmidrule(r){4-5}
                                               & £        & £       & £      & £      \\
{\bf Fixed Assets}                             &          &         &        &        \\
{\bf Tangible fixed assets}                    &          & 5,149   &        & 5,525  \\
\cmidrule(r){2-3} \cmidrule(r){4-5} \\
{\bf Current Assets}                           &          &         &        &        \\
Rental Deposit                                 & 7,696    &         & 7,696  &        \\
Inventory                                      & 163      &         & 0      &        \\
Cash at bank and in hand                       & 14,889   &         & 7,688  &        \\
Creditors: amounts falling due within one year & -167     &         & -2,511 &       \\
Prepaid Subscriptions                          & 0        &         & -610   &       \\
{\bf Net current assets}                       &          & 27,898  &        & 12,263 \\
\cmidrule(r){2-3} \cmidrule(r){4-5} \\
{\bf Total assets less current liabilities}    &          & 27,732  &        & 17,787 \\
\cmidrule(r){2-3} \cmidrule(r){4-5}  \\
{\bf Capital and Reserves}&\\
Income and expenditure account                 &          & 27,732  &        & 17,787 \\
\bottomrule
\end{tabular}

@@

Approved by the Board for issue on TBC
\vspace{48pt}

>>>>

\begin{center}
\begin{tabular}{  l  r  r r r}
\toprule
                            & \multicolumn{2}{c}{2012} &  \multicolumn{2}{c}{2011} \\
\cmidrule(r){2-3} \cmidrule(r){4-5}
                                               & £        & £       & £      & £      \\
{\bf Fixed Assets}                             &          &         &        &        \\
{\bf Tangible fixed assets}                    &          & 5,149   &        & 5,525  \\
\cmidrule(r){2-3} \cmidrule(r){4-5} \\
{\bf Current Assets}                           &          &         &        &        \\
Rental Deposit                                 & 7,696    &         & 7,696  &        \\
Inventory                                      & 463      &         & 0      &        \\
Cash at bank and in hand                       & 14,889   &         & 7,688  &        \\
Creditors: amounts falling due within one year & -167     &         & -2,511 &       \\
Prepaid Subscriptions                          & 0        &         & -610   &       \\
{\bf Net current assets}                       &          & 22,881  &        & 12,263 \\
\cmidrule(r){2-3} \cmidrule(r){4-5} \\
{\bf Total assets less current liabilities}    &          & 28,030  &        & 17,787 \\
\cmidrule(r){2-3} \cmidrule(r){4-5}  \\
{\bf Capital and Reserves}&\\
Income and expenditure account                 &          & 28,030  &        & 17,787 \\
\bottomrule
\end{tabular}

@@

Approved by the Board for issue on the 27\superscript{th} December 2012.
\vspace{48pt}
